Reconstructing Rearrangement Phylogenies of Natural Genomes

### 2023-10-24 docs/manuscript/main.tex
intermediate save

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%

\section{Introduction}
\section{Background}
\subsection{Problem Formulation}
\section{A new Method}
\subsection{Pre-selecting Adjacencies}
\todoDany{Describe Process}
\subsection{A New ILP Formulation}

\include{ilp}
\section{Evaluation}
\section{Discussion}

>>>>

\keywords{genome rearrangement \and ancestral reconstruction \and small parsimony \and integer linear programming \and double-cut-and-join}
\end{abstract}

%\section{Introduction}
\section{Background}

\begin{itemize}
    \item SPP algoirthms such as 
\end{itemize}
\section{A new Method}
\subsection{Preliminaries}
General notation
\begin{itemize}
    \item Weighted multigraph $G = (\vertices, \edges, \w)$ with edge weight function $\w: \edges \to \mathbb R$
    \item A \emph{phylogeny} $\tree$ is a connected graph. Nodes of $\tree$ with degree 1 are termed \emph{leaves}.
\end{itemize}

Paper-specific notation:

\begin{itemize}
    \item Genomic marker 
    \item Genome $\X$
    \item Genome adjacency graph $\ggraph(\X) = (V, \adjacencyedges)$ \todoDany{find better name?}
    \item 
We model family assignments of marker extremities as a function $\family: \extremities \to \mathbb N$ for which holds true that for any marker $g = \{g^\et, g^\eh\}$, $\family(g^\et) = \family(g^\eh)$.  
Function 
$\minmulti_\X\varepsilon)$ reports the minimum multiplicity of the marker corresponding to extremity $\varepsilon$ in a given genome $\X$, while $\maxmulti_\X(\varepsilon)$ reports its maximum multiplicity. 
A family assignment $\family'$ is \emph{$\family$-derived} if there exists no two extremities $\varepsilon, \varepsilon'$ with $\family'(\varepsilon) = \family'(\varepsilon')$ and $\family(\varepsilon) \neq \family(\varepsilon')$.  
A family assignment $\family$ is termed \emph{$\mathcal \A$-resolved} (or simply \emph{resolved} if the context is clear) if for each member $\X$ of a set of genomes $\mathcal A$, each extremity $\varepsilon \in \extremities $ has a multiplicity not higher than $1$, \emph{i.e.}, $\maxmulti_\X(\varepsilon)\leq 1$.

    \item Multirelational diagram $\mrd$ and \emph{capping-free multi-relational diagram} (CFMRD) $\pcmrd$
\end{itemize}
\subsection{Pre-selecting Adjacencies}
\todoDany{Describe Process}
\subsection{A New ILP Formulation}
The algorithm described in the following operates on two levels: 
on the local level, a genome is derived from each genome adjacency graph, constituting a set of linear or circular chromosomes. 
On the global level, genomes are connected to each other along the branches of the phylogeny. Each branch gives rise to a pairwise comparison by means of the CFMRD. 
In doing so, the selection of adjacencies of a derived genome is propagated from across CFMRDs, thus ensuring global consistency.

\paragraph{Local level.} Constraint \ref{c:cn}

\paragraph{Global level.}
When comparing pairs of genomes within a CFMRD, we make use of a capping-free formulation for the computation of the pairwise DCJ indel distance~\cite{BOH-2023}.

\todoLeo{Insert a description of the formulation here}

\include{ilp}

\section{Evaluation}
\section{Discussion}
